Refinements for open pNets

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
sat

 We suppose given a decidable satisfiability relation on formulas, \({\vdash} f\) is the satisfiability over closed formulas.
% In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
%\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
We will  use two satisfiability relations:
\begin{itemize}
\item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\):
\( \sigma \vdash f ::= \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
\item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context:
\( V \vdash f ::=  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
\end{itemize}

@@

\section{A First Refinement Relation}\label{sec:refinement}
\TODO{4 pages}

>>>>

 We suppose given a decidable satisfiability relation on formulas, \({\vdash} f\) is the satisfiability over closed formulas.
% In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
%\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
We will  use two satisfiability relations:
\begin{itemize}
\item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is defined as follows:
\( \sigma \vdash f ::= \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
\item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is defined as follows:
\( V \vdash f ::=  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
\end{itemize}

@@

\section{A First Refinement Relation}\label{sec:refinement}

deadlock and reachability

Hole - = relation

\TODO{4 pages}
